Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
update

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
%
\citet{LaMassa2017, Glikman2018, LaMassa2019} 
%

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux. 1 objects is in common to both, so this sample of 32 is our starting point for variability investigations. The common object is VIK J1148+0056. 
%% is SDSSJ0958+3524 special at all??

@@

Then calculate the clipped median and standard deviation, 
\begin{equation}
1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
%%
With this definition, although some of the objects have very well sampled, 
`average' light curves where you are averaging over e.g. a month, or two weeks.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
%
Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
several investigations have looked at how WISE detects AGN 
\citet[e.g][Secrest2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019} 
%

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, we find there are 21 WFCAM and 12 VISTA objects with at least 8 measurements observed with durations over 30 days, in at least one filter and with the average calibrated flux is greater than 0 and at least $8\times$ the error on the average calibrated flux. 1 objects is in common to both, so this sample of 32 is our starting point for variability investigations. The common object is VIK J1148+0056.

@@

The clipped median and standard deviation is then ncalculated, 
\begin{equation}
1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
%%
With this definition, although some of the objects have very well sampled, 
``average'' light curves where you are averaging over e.g. a month, or two weeks.
